---
title: "Introduction to pkgpeanuts"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to pkgpeanuts}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, comment = "#>", fig.path = "man/figures/README-", eval = TRUE,
  message = FALSE, warning = FALSE, error = FALSE, tidy = TRUE
)
```

The intent of `pkgpeanuts` is to automate building out robust R package scaffolding for a newly created package. Create a new R package project in RStudio. Make an initial commit and link up the local repository with your empty remote repository. Then let `pkgpeanuts` take care of the rest. It is important to note that the primary function `pkgpeanuts::pour` is not intended for existing packages.

## Package setup

If this has not been done, pkgpeanuts will likely fail. Its use will become less problematic later, but currently there are issues yet to be worked out.

Once this minimal setup is complete, call `pkgpeanuts::pour` from the package root directory with your desired arguments. I suggest not doing this, however. Instead, use the RStudio addin.

pkgpeanuts has many arguments. See the help documentation for details. And again, this is not intended for existing packages.
Note that if you provide `lintr = "test"` and receive a warning like the following:

```
In file.symlink("inst/.lintr", ".lintr") :
  cannot symlink 'inst\.lintr' to '.lintr', reason 'A required privilege is not held by the client'
```

this means that `pour` was unable to create a symlink due to restricted permissions. You need to run RStudio as administrator to avoid this warning. The symbolic link is necessary for the current approach to combining `lintr` with `testthat` unit testing and not failing a Travis-CI build. I think there is now another way to do this, but I have not looked into it yet. Stay tuned.

## Shiny apps in a package

Add an existing, external Shiny app to a source package with `use_app`. This will copy the app into the `inst` directory. For example:

```{r use_app, eval=FALSE}
use_app("../app")
```

By default this will also add a template `DESCRIPTION` file and template `Readme.md` file. These files can also be added separately using `use_app_description` and `use_app_readme`. This gives more control over the content output by `use_app_description`. These files are useful for Shiny showcase mode.

```{r use_templates, eval=FALSE}
use_app_description("path/to/app", title = "My app", author = "Me", url = "example.com", tags = c("data analysis", "graphing"))
use_app_readme()
```
