---
title: "Introduction to pkgpeanuts"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to pkgpeanuts}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, comment = "#>", fig.path = "man/figures/README-", eval = TRUE,
  message = FALSE, warning = FALSE, error = FALSE, tidy = TRUE
)
```

The intent of `pkgpeanuts` is to automate building out robust R package scaffolding for a newly created package. Create a new R package project in RStudio. Make an initial commit and link up the local repository with your empty remote repository. Then let `pkgpeanuts` take care of the rest. It is important to note that the primary function `pkgpeanuts::pour` is not intended for existing packages.

## Package setup

After creating a new package in RStudio, make sure the new, empty repository exists on GitHub (or BitBucket) as well. Make an initial commit, e.g. commit the `.Rproj` file, so that you can add and push to the remote repository. If this has not been done, `pkgpeanuts` will fail. Once this minimal setup is complete, run something like the following from the package root directory:

```{r pkgpeanuts, eval=FALSE}
pkgpeanuts::pour(path = ".", account = "github_username", name = "My Name")
```

`pkgpeanuts` has many arguments. See the help documentation for details. And again, this is not intended for existing packages.

Note that if you provide `lintr = "test"` and receive a warning like the following:

```
In file.symlink("inst/.lintr", ".lintr") :
  cannot symlink 'inst\.lintr' to '.lintr', reason 'A required privilege is not held by the client'
```

this means that `pour` was unable to create a symlink due to restricted permissions. You need to run RStudio as administrator to avoid this warning. The symbolic link is necessary for the current approach to combining `lintr` with `testthat` unit testing and not failing a Travis-CI build. I think there is now another way to do this, but I have not looked into it yet. Stay tuned.

## Shiny apps in a package

Add an existing, external Shiny app to a source package with `use_app`. This will copy the app into the `inst` directory. For example:

```{r use_app, eval=FALSE}
use_app("../app")
```

By default this will also add a template `DESCRIPTION` file and template `Readme.md` file. These files can also be added separately using `use_app_description` and `use_app_readme`. This gives more control over the content output by `use_app_description`. These files are useful for Shiny showcase mode.

```{r use_templates, eval=FALSE}
use_app_description("path/to/app", title = "My app", author = "Me", url = "example.com", tags = c("data analysis", "graphing"))
use_app_readme()
```
